---
title: "Replication package-RSiena"
author: '[Jochem Tolsma](https://www.jochemtolsma.nl) - Radboud University / University of Groningen, the Netherlands'
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    toc:  true
    toc_float: true
    number_sections: false
    code_folding: hide
    code_download: yes
---


```{r globalsettings, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, echo=FALSE, eval=FALSE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r colorize, echo=FALSE, eval=TRUE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
            x)
  } else x
}

```

```{r klippy, echo=FALSE, include=TRUE, eval=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{css, echo=FALSE}

pre.test {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
}

pre.test2 {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
  background-color: white;
  color: rgb(201, 76, 76);
}


h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
}

```



---  


# Intro  


This [website](https://jochemtolsma.github.io/Twitter/) is a replication package for the paper "**How Twitter divides the Dutch parliament: Segregation along party lines and social dimensions in the following, @-mentions and retweets Twitter Networks of Dutch MPs**" by @Tolsma2021.

It contains R code to replicate all Tables/Figures/Appendix in the manuscript.

To copy the code click the button in the upper right corner of the code-chunks.

Use the top menu to navigate to the section of interest. 

The source code of this website can be found on [Github](https://github.com/JochemTolsma/Twitter)

Questions can be addressed to [Jochem Tolsma](mailto:jochem.tolsma@ru.nl).

---  

## Packages  

```{r packages, echo=TRUE, message=FALSE, warning=FALSE, eval=TRUE}
#install if necessary 
if (!require("tidyverse", character.only = TRUE)) {install.packages("tidyverse", dependencies=TRUE)}
if (!require("dplyr", character.only = TRUE)) {install.packages("dplyr", dependencies=TRUE)}
if (!require("foreign", character.only = TRUE)) {install.packages("foreign", dependencies=TRUE)}
if (!require("igraph", character.only = TRUE)) {install.packages("igraph", dependencies=TRUE)}
if (!require("knitr", character.only = TRUE)) {install.packages("knitr", dependencies=TRUE)}
if (!require("kableExtra", character.only = TRUE)) {install.packages("kableExtra", dependencies=TRUE)}
if (!require("RSiena", character.only = TRUE)) {install.packages("RSiena", dependencies=TRUE)}
if (!require("haven", character.only = TRUE)) {install.packages("haven", dependencies=TRUE)}

#load packages.
library(tidyverse)
library(dplyr)
library(foreign)
library(igraph)
library(knitr)
library(kableExtra)
library(RSiena)
library(haven)


```


---   



## Custom functions: tweaking output


```{r, echo=TRUE, eval=TRUE}

fanscsv <- function(ans=ans) {
	ans1_mat <- matrix(NA, nrow=length(ans$effects[,2]),ncol=3)
	row.names(ans1_mat) <- ans$effects[,2]
	ans1_mat[,1] <- (ans$theta)
	ans1_mat[,2] <- (ans$se)
	ans1_mat[,3] <- (ans$tconv)
	ans1_mat <- rbind(ans1_mat, c(ans$tconv.max))
	row.names(ans1_mat)[length(row.names(ans1_mat))] <- "Overall maximum convergence ratio:"
	colnames(ans1_mat) <- c("Estimate", "Standard Error", "Convergence t-ratio")
	return(ans1_mat)
	#print(ans1_mat)
	#write.csv(ans1_mat, filename)
}




```

---  

## Load data objects {.tabset .tabset-fade}  


Data objects:  

- [key](./data-processed/key moederbestand 20171114.sav): information on all politicians on election list  
- [twitter](./data-processed/twitter_20190919.RData)  
    - keyf: information on all 147 MPs with twitter handle  
    - mydata: RSiena object with all kind of goodies inside  
    - seats: seating coordinates of HoP (used for plotting)  
- [CHES](https://www.chesdata.eu/ches-europe): information on party positions see also [@jolly2022chapel]


```{r, eval=TRUE}
library(haven)
ches <- read_dta("./data-raw/CHES_means_2017.dta")
ches <- as.data.frame(ches)
ches <- ches[ches$country==10,]
```


As the ideological position of parties was not included in our original data object we need to fix that. 

```{r data, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
#STAP 1: read in data
key <- read.spss('data-processed\\key moederbestand 20171114.sav', use.value.labels=T, to.data.frame=T)


load("data-processed\\twitter_20190919.RData")
#str(twitter_20190919,1)
keyf <- twitter_20190919[[1]]
mydata <- twitter_20190919[[2]]
seats <- twitter_20190919[[3]]

ches$Partij <- ches$party

keyf <- left_join(keyf, ches)

#deconstruct dataobject
deps <- mydata$depvars
covariates <- mydata$cCovars
codyadcovar <- mydata$dycCovars

fnet <- sienaNet(deps$fnet) 
atmnet <- sienaNet(deps$atmnet)
rtnet <- sienaNet(deps$rtnet)
afstand <- codyadcovar$afstand
egohandle <- covariates$egohandle
egoid <- covariates$egoid
partij <- covariates$partij
coalitie <- covariates$coalitie
cda <- covariates$cda
cu <- covariates$cu
denk <- covariates$denk
d66 <- covariates$d66
fvd <- covariates$fvd
gl <- covariates$gl
pvda <- covariates$pvda
pvdd <- covariates$pvdd
pvv <- covariates$pvv
sgp <- covariates$sgp
sp <- covariates$sp
vvd <- covariates$vvd
plus <- covariates$plus
ethminz <- covariates$ethminz
vrouw <- covariates$vrouw
lft <- covariates$lft
kamerlid2016 <- covariates$kamerlid2016
kabinet2016 <- covariates$kabinet2016
pleklijst <- covariates$pleklijst
pleklijst1 <- covariates$pleklijst1
#add new variable
partypos <- coCovar(keyf$lrgen)  

#reconstruct dataobject
mydata_RR <- sienaDataCreate(fnet,
                          atmnet, 
                          rtnet, 
                          afstand, 
                          egohandle, 
                          egoid, 
                          partij, 
                          coalitie, 
                          cda,
                          cu,
                          denk,
                          d66,
                          fvd,
                          gl,
                          pvda,
                          pvdd,
                          pvv,
                          sgp,
                          sp,
                          vvd,
                          plus, 
                          ethminz,
                          vrouw,
                          lft,
                          kamerlid2016,
                          kabinet2016,
                          pleklijst,
                          pleklijst1,
                          partypos)


```


---  

# Impact of ideological distance 

An anonymous reviewer suggested to try to disentangle the impact of physical seating distance from ideological distance. We therefore added to the party to which each MP belongs a general left-right position according to the Chapel Hill Survey [@jolly2022chapel]. 

## define effects  

```{r echo=TRUE, eval=TRUE, results='hide'}
myeff <- getEffects( mydata_RR )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
#myeff_m2 <- setEffect( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet", fix=TRUE, initialValue = -3, test=TRUE )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )

myeff_RR <- myeff_m2
myeff_RR <- includeEffects(myeff_RR, interaction1="partypos", absDiffX, name="fnet" )
myeff_RR <- includeEffects(myeff_RR, interaction1="partypos", absDiffX, name="rtnet" )
```


```{r echo=TRUE, eval=TRUE}
myeff_RR
```

## estimate model

```{r, echo=TRUE, eval=FALSE}
myalgorithmRR <- sienaAlgorithmCreate( projname = 'RR')

ansRR1 <- siena07( myalgorithmRR, data = mydata_RR, prevAns=ansM8c, effects = myeff_RR, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)

#save(ansRR1, file=paste("ansRR1",".RData",sep=""))
```
## results  

The parameters of interest are in red. 


```{r, echo=TRUE, eval=TRUE}
load("ansRR1.RData")


res <- round(fanscsv(ansRR1)[,1:2],5)
mcpos <- length(res[,1])
res <- res[-mcpos,]
mc <- as.character(round(fanscsv(ansRR1)[mcpos,1],3))
row.names(res) <- c(
 "rate 1"  ,      
 "rate 2"   ,     
 "outdegree"          ,  
 "reciprocity"         ,           
 "transitive triplets"  ,          
 "shared popularity"     ,         
 "indegree - popularity"   ,
  " outdegree - popularity" , 
 "outdegree - activity"    ,
 "seating distance (dyad)"         ,               
 "same party (dyad)"                ,    
"incumbancy status (alter)"          ,   
"same incumbancy status (dyad)"       ,       
"position on election list (ego)"      ,
"ideological distance (dyad)" ,
 "rate 1"      ,
 "rate 2"      ,
"outdegree"          ,
 "reciprocity"        ,          
 "transitive triplets" ,         
 "shared popularity"    ,        
 "indegree - popularity" ,
 "outdegree - popularity",
"outdegree - activity "  ,
 "same party (dyad)"            ,      
"party Liberal Democrats (alter)",                    
"party GreenLeft (alter)"         ,            
 "party GreenLeft (ego)"           ,            
 "position on election list (alter)",              
"party leader (alter)"             ,
 "party leader (ego)"               ,
 "rate 1"       ,
 "rate 2"       ,
"outdegree"           ,
"reciprocity"          ,         
"transitive triplets"   ,        
"shared popularity"      ,       
"indegree - popularity ",  
"outdegree - popularity", 
"outdegree - activity "   ,
"seating distance (dyad)"        ,               
 "same party (dyad)"              ,     
 "party Liberal Democrats (ego)"   ,                    
 "party Freedom Party (ego)"        ,               
 "incumbancy status (alter)"         ,   
 "incumbancy status (ego)"            ,  
 "position on election list (alter)"   ,            
"party leader (alter)", 
 "ideological distance (dyad)"
)
  
asmatkable <- kbl(res, booktabs=TRUE, digits=3, caption="Model RR: including ideological distance", align = "c") %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(column = 1, width = "3in")   %>%
  row_spec(c(10, 15,41,49), bold = T, color = "white", background = "#D7261E") %>%
  group_rows(index = c("Following" = 15, "Atmention" = 16, "Retweets" = 18)) %>%
  footnote(general = paste("Overall maximum convergence ratio: ", mc, sep="" ))


asmatkable


```

---  

# References  


