---
title: "Replication package-Figures"
author: '[Jochem Tolsma](https://www.jochemtolsma.nl) - Radboud University / University of Groningen, the Netherlands'
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    toc:  true
    toc_float: true
    number_sections: false
    code_folding: hide
    code_download: yes
---

```{r globalsettings, echo=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, echo=FALSE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r colorize, echo=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
            x)
  } else x
}

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{css, echo=FALSE}
pre.test {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
}

pre.test2 {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
  background-color: white;
  color: rgb(201, 76, 76);
}


h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
}


```



------------------------------------------------------------------------

<!---als figuurtjes goed zijn, zet dan eval=FALSE--->


# Intro  


This [website](https://jochemtolsma.github.io/Twitter/) is a replication package for the paper "Twitter" by @Tolsma2021.

It contains R code to replicate all Tables/Figures/Results in the manuscript.

To copy the code click the button in the upper right corner of the code-chunks.

Use the top menu to navigate to the section of interest. 

The source code of this website can be found on [Github](https://github.com/JochemTolsma/Twitter)

Questions can be addressed to [Jochem Tolsma](mailto:jochem.tolsma@ru.nl).

---  

## Packages  

```{r packages, echo=TRUE}
#install if necessary 
if (!require("dplyr", character.only = TRUE)) {install.packages("dplyr", dependencies=TRUE)}
if (!require("foreign", character.only = TRUE)) {install.packages("foreign", dependencies=TRUE)}
if (!require("RSiena", character.only = TRUE)) {install.packages("RSiena", dependencies=TRUE)}

#load packages.
library(tidyverse)
library(dplyr)
library(foreign)
library(RSiena)
library(knitr)
library(kableExtra)

```


---   

## Custom functions

siena07ToConvergence: sie RSiena Manual p 69 

```{r}
siena07ToConvergence <- function(alg, dat, eff, ans0=NULL, ...){
  numr <- 0
  ans <- siena07(alg, data=dat, effects=eff, prevAns=ans0, ...) # the first run
  repeat {
    save(ans, file=paste("ans",numr,".RData",sep="")) # to be safe
    numr <- numr+1 # count number of repeated runs
    tm <- ans$tconv.max # convergence indicator
    cat(numr, tm,"\n") # report how far we are
    if (tm < 0.25) {break} # success
    if (tm > 10) {break} # divergence without much hope of returning to good parameter values
    if (numr > 30) {break} # now it has lasted too long
    ans <- siena07(alg, data=dat, effects=eff, prevAns=ans, ...)
    }
  if (tm > 0.25)
  {
    cat("Warning: convergence inadequate.\n")
  }
  ans
}
```


## Load data objects {.tabset .tabset-fade}  

See ... for construction of data objects.  

Data objects:  

- key: information on all politicians on election list  
- keyf: information on all 147 MPs with twitter handle  
- mydata: RSiena object with all kind of goodies inside  
- seats: seating coordinates of HoP (used for plotting)

```{r data, echo=TRUE}
#STAP 1: read in data
key <- read.spss('data-processed\\key moederbestand 20171114.sav', use.value.labels=T, to.data.frame=T)


load("data-processed\\twitter_20190919.RData")
#str(twitter_20190919,1)
keyf <- twitter_20190919[[1]]
mydata <- twitter_20190919[[2]]
seats <- twitter_20190919[[3]]


```

---  



## Baseline model (structural effects only)

Included effects:  

- three dependent network variables  
- degree (with or without time heterogeneity)  
- reciprocity  
- indegree-popularity (sqrt)  
- outdegree-activity (sqrt)  
- outdegree-popularity (sqrt)  
- transitive triplets or GWESPP  

We further test for two additional effects: 
-   
- shared popularity

```{r structural model }
print01Report( mydata, modelname="Twitter")
#let us have a look at all possible effects
#effectsDocumentation()
```

Define the model

We will compare a model with *transTrip* versus *gwespFF* first. 

### transTrip

#### Effects. 

```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

#myeff_m1 <- includeEffects( myeff_m1, cycle3, name="fnet" )
#myeff_m1 <- includeEffects( myeff_m1, cycle3, name="atmnet" )
#myeff_m1 <- includeEffects( myeff_m1, cycle3, name="rtnet" )


```

#### Estimate. 

Models:  

- ansM1  
- ansM1b  

```{r, eval=FALSE}
myalgorithm <- sienaAlgorithmCreate( projname = 'M1')
ansM1 <- siena07( myalgorithm, data = mydata, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1

ansM1b <- siena07( myalgorithm, data = mydata, prevAns=ansM1, effects = myeff_m1, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)

ansM1b ##good fit. 

save(ansM1b, file=paste("ansM1b",".RData",sep=""))

```

---  

### time heterogeneity in outdegree. 

#### Effects  


```{r}

myeff_m1 <- myeff

meff_m1
myeff_m1_td <- includeTimeDummy(myeff_m1, density, name="atmnet", timeDummy="2")
myeff_m1_td <- includeTimeDummy(myeff_m1_td, density, name="rtnet", timeDummy="2")


```

#### Estimates
```{r, eval=FALSE}

ansM2 <- siena07( myalgorithm, data = mydata, prevAns=ansM1b, effects = myeff_m1_td, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM2 
save(ansM2, file=paste("ansM2",".RData",sep=""))

ansM2b <- siena07( myalgorithm, data = mydata, prevAns=ansM2, effects = myeff_m1_td, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM2b 
save(ansM2b, file=paste("ansM2b",".RData",sep=""))

```



---  

### gwespFF

#### Effects  

```{r, eval=FALSE}
myeff <- getEffects( mydata )
myeff_m1b <- myeff

#according to suggestion of rsiena manual
myeff_m1b <- includeEffects( myeff_m1b, inPopSqrt, name="fnet" )
myeff_m1b <- includeEffects( myeff_m1b, inPopSqrt, name="atmnet" )
myeff_m1b <- includeEffects( myeff_m1b, inPopSqrt, name="rtnet" )

myeff_m1b <- includeEffects( myeff_m1b, outActSqrt, name="fnet" )
myeff_m1b <- includeEffects( myeff_m1b, outActSqrt, name="atmnet" )
myeff_m1b <- includeEffects( myeff_m1b, outActSqrt, name="rtnet" )

myeff_m1b <- includeEffects( myeff_m1b, outPopSqrt, name="fnet" )
myeff_m1b <- includeEffects( myeff_m1b, outPopSqrt, name="atmnet" )
myeff_m1b <- includeEffects( myeff_m1b, outPopSqrt, name="rtnet" )

myeff_m1b <- includeEffects( myeff_m1b, gwespFF, name="fnet" )
myeff_m1b <- includeEffects( myeff_m1b, gwespFF, name="atmnet" )
myeff_m1b <- includeEffects( myeff_m1b, gwespFF, name="rtnet" )

myeff_m3 <- myeff_m1b

``` 

#### Estimate  

Models:  

- ansM3  
- ansM3b  

```{r}
myalgorithm <- sienaAlgorithmCreate( projname = 'M1')
ansM3 <- siena07( myalgorithm, data = mydata, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM3
save(ansM3, file=paste("ansM3",".RData",sep=""))

ansM3b <- siena07( myalgorithm, data = mydata, prevAns=ansM3, effects = myeff_m1, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM3b  
save(ansM1d, file=paste("ansM3b",".RData",sep=""))

```

---  


### include sharedPop (transTrip)

#### Effects.  

```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

```

#### Estimate

Models (build on ansM1b):  

- ansM4  
- ansM4b  

```{r}

load("ansM1b.RData")

ansM4 <- siena07( myalgorithm, data = mydata, prevAns=ansM1b, effects = myeff_m1, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM4 
save(ansM4, file=paste("ansM4",".RData",sep=""))

ansM4b <- siena07( myalgorithm, data = mydata, prevAns=ansM4, effects = myeff_m1, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM4b
save(ansM4b, file=paste("ansM4b",".RData",sep=""))

```

----  

## Baseline model (with covariates)

### All covariates

#### Effects  

We cannot include all party dummies as covariates for ego and alter. We will thus first check which party deviates significantly with respect to indegree and outdegree. 

First the descriptives. 
```{r}
#check if we observe outdegree differences per partij
fnet <- mydata$depvars$fnet
atmnet <- mydata$depvars$atmnet
rtnet <- mydata$depvars$rtnet
testfnet <- fnet[,,1]
testfnet[testfnet==10] <- NA
testrtnet <- rtnet[,,1]
testrtnet[testrtnet==10] <- NA
testatmnet <- atmnet[,,1]
testatmnet[testatmnet==10] <- NA

keyf$outdegreesf <- rowSums(testfnet, na.rm=TRUE)
keyf$indegreesf <- colSums(testfnet, na.rm=TRUE)

keyf$outdegreesrt <- rowSums(testrtnet, na.rm=TRUE)
keyf$indegreesrt <- colSums(testrtnet, na.rm=TRUE)

keyf$outdegreesatm <- rowSums(testatmnet, na.rm=TRUE)
keyf$indegreesatm <- colSums(testatmnet, na.rm=TRUE)


degreesum <- keyf %>% 
  group_by(Partij) %>%
  summarize(mean_of= mean(outdegreesf, na.rm=T),
            mean_if= mean(indegreesf, na.rm=T),
            mean_irt= mean(outdegreesrt, na.rm=T),
            mean_ort= mean(indegreesrt, na.rm=T),
            mean_iat= mean(outdegreesatm, na.rm=T),
            mean_oat= mean(indegreesatm, na.rm=T),
            count= n()) %>%
  arrange(desc(count)) %>%
  select(!("count"))


colnames(degreesum) <- c("Party", "outdegree friends", "indegree friends", "outdegree retweets", "indegree retweets", "outdegree atmentions", "indegree atmentions")


write_csv(degreesum, "degreesum.csv")

degreesum <- kbl(degreesum, booktabs=TRUE, digits=2, caption="mean degree by party", align = "c") %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) 

scroll_box(degreesum, width="100%", height="500px")

```

Let us use a simple OLS regression with deviation coding (grand mean is ref) to test for significance.
```{r, results="hold"}

keyf$Partij2 <- as.factor(as.character(keyf$Partij))
levels(keyf$Partij2)
contrasts(keyf$Partij2) <- contr.sum(13) #let us use VVD as omitted party

summary(lm(outdegreesf~Partij2, keyf))
print("which parties deviate significantly outdegreesf")
levels(keyf$Partij2)[c(1, 6, 9, 10, 11)]

summary(lm(indegreesf~Partij2, keyf))
print("which parties deviate significantly indegreesf")
levels(keyf$Partij2)[c(10, 11)]

summary(lm(outdegreesatm~Partij2, keyf))
print("which parties deviate significantly outdegreesatm")
levels(keyf$Partij2)[c(4, 7, 10, 12)]

summary(lm(indegreesatm~Partij2, keyf))
print("which parties deviate significantly indegreesatm")
levels(keyf$Partij2)[c(4, 7, 10)]

summary(lm(outdegreesrt~Partij2, keyf))
print("which parties deviate significantly outdegreesrt")
levels(keyf$Partij2)[c(1, 4, 7, 10)]

summary(lm(indegreesrt~Partij2, keyf))
print("which parties deviate significantly indegreesrt")
levels(keyf$Partij2)[c(4, 10)]

```




```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



#myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )



```

#### Estimates

```{r}
load("ansM4b.RData")
myalgorithm <- sienaAlgorithmCreate( projname = 'M2')
ansM5 <- siena07( myalgorithm, data = mydata, prevAns=ansM4b, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM5 
save(ansM5, file=paste("ansM5",".RData",sep=""))

ansM5b <- siena07( myalgorithm, data = mydata, prevAns=ansM5, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM5b 
save(ansM5b, file=paste("ansM5b",".RData",sep=""))
```

---  

### lets trim

I forgot to include sameX Party for fnet. will include now. 

```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )



```

#### Estimates

```{r}
load("ansM4b.RData") #start again from ansM4b
myalgorithm <- sienaAlgorithmCreate( projname = 'M3')
ansM6 <- siena07( myalgorithm, data = mydata, prevAns=ansM4b, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM6 
save(ansM6, file=paste("ansM6",".RData",sep=""))

ansM6b <- siena07( myalgorithm, data = mydata, prevAns=ansM6, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM6b 
save(ansM6b, file=paste("ansM6b",".RData",sep=""))
```



### second trim


```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )



```

#### Estimates

```{r}
load("ansM4b.RData") #start again from ansM4b
myalgorithm <- sienaAlgorithmCreate( projname = 'M4')
ansM7 <- siena07( myalgorithm, data = mydata, prevAns=ansM4b, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM7 # Overall maximum convergence ratio:    0.2501 
save(ansM7, file=paste("ansM7",".RData",sep=""))

ansM7b <- siena07( myalgorithm, data = mydata, prevAns=ansM7, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM7b # Overall maximum convergence ratio:    0.2422 
save(ansM7b, file=paste("ansM7b",".RData",sep=""))

load("ansM7b.RData")

ansM7c <- siena07( myalgorithm, data = mydata, prevAns=ansM7, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM7c 
save(ansM7c, file=paste("ansM7c",".RData",sep=""))
```


### third trim

#### Effects  

```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
#myeff_m2 <- setEffect( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet", fix=TRUE, initialValue = -3, test=TRUE )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )



```

#### Estimates

```{r}
load("ansM8c.RData") #start again from ansM4b
ansM4b
myalgorithm <- sienaAlgorithmCreate( projname = 'M5')
ansM8 <- siena07( myalgorithm, data = mydata, prevAns=ansM4b, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM8 
save(ansM8, file=paste("ansM8",".RData",sep=""))

ansM8b <- siena07( myalgorithm, data = mydata, prevAns=ansM8, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM8b 
save(ansM8b, file=paste("ansM8b",".RData",sep=""))

ansM8c <- siena07( myalgorithm, data = mydata, prevAns=ansM8b, effects = myeff_m2, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM8c #Overall maximum convergence ratio:    0.2471 

save(ansM8c, file=paste("ansM8c",".RData",sep=""))
```

## Social inbreeding homophily

### Effects 


```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
#myeff_m2 <- setEffect( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet", fix=TRUE, initialValue = -3, test=TRUE )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )

myeff_m3 <- myeff_m2

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="atmnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="atmnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="atmnet" )



```

### Estimates

```{r}
load("ansM8c.RData") 

myalgorithm <- sienaAlgorithmCreate( projname = 'M9')
ansM9 <- siena07( myalgorithm, data = mydata, prevAns=ansM8c, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM9 
save(ansM9, file=paste("ansM9",".RData",sep=""))

ansM9b <- siena07( myalgorithm, data = mydata, prevAns=ansM9, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM9b 
save(ansM9b, file=paste("ansM9b",".RData",sep=""))

ansM9c <- siena07( myalgorithm, data = mydata, prevAns=ansM9b, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM9c 

save(ansM9c, file=paste("ansM9c",".RData",sep=""))
```

## Trim social inbreeding homophily 

Only ego alter. we leave dyad in. 

### Effects 


```{r}
myeff <- getEffects( mydata )
myeff_m1 <- myeff

#according to suggestion of rsiena manual
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, inPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outActSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, outPopSqrt, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, transTrip, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, transTrip, name="rtnet" )

myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="fnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="atmnet" )
myeff_m1 <- includeEffects( myeff_m1, sharedPop, name="rtnet" )

myeff_m2 <- myeff_m1

#"kamerlid2016" "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
#myeff_m2 <- setEffect( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet", fix=TRUE, initialValue = -3, test=TRUE )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", sameX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", egoX, name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", altX, name="rtnet" )

#these need to be dropped due to collinearity
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

#afstand
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )



myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="fnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="fnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="atmnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="atmnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="atmnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="atmnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="atmnet" )

myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "partij", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "denk", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvdd", name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, egoX, interaction1 = "plus", name="rtnet" )

#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "cu", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "denk", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "d66", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "fvd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "gl", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvda", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvdd", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "pvv", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sgp", name="rtnet" )
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "sp", name="rtnet" )
# myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "vvd", name="rtnet" ) #referentie
#myeff_m2 <- includeEffects( myeff_m2, altX, interaction1 = "plus", name="rtnet" )

myeff_m3 <- myeff_m2

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="atmnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="rtnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="atmnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="rtnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="atmnet" )



```



### Estimates

```{r}
load("ansM8c.RData") 

myalgorithm <- sienaAlgorithmCreate( projname = 'M10')
ansM10 <- siena07( myalgorithm, data = mydata, prevAns=ansM8c, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM10 
save(ansM10, file=paste("ansM10",".RData",sep=""))

ansM10b <- siena07( myalgorithm, data = mydata, prevAns=ansM10, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM10b 
save(ansM10b, file=paste("ansM10b",".RData",sep=""))

ansM10c <- siena07( myalgorithm, data = mydata, prevAns=ansM10b, effects = myeff_m3, useCluster=TRUE, nbrNodes=8, initC=TRUE, batch=TRUE)
ansM10c 

save(ansM9c, file=paste("ansM9c",".RData",sep=""))
```



<!---


myeff_m2 <- includeEffects(myeff_m1, egoX, interaction1 = "cda", name="fnet" )

save(myeff_m1, file="myeff_m1.Rdata")
}
#estimate model
{
# Estimate parameters
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff_m1.Rdata")
ansM1 <- siena07( myalgorithm, data = mydata, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1
ansM1b <- siena07( myalgorithm, data = mydata, prevAns=ansM1, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1b
ansM1c <- siena07( myalgorithm, data = mydata, prevAns=ansM1b, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1c
save(ansM1c, file="ansM1c.Rdata")
}
```


#print01Report( mydata, modelname="Reporttwitter_20190829")
#let us have a look at all possible effects
#effectsDocumentation()

###model 1: define myeff_m1
{

#check if we observe outdegree differences per partij
fnet <- mydata$depvars$fnet
atmnet <- mydata$depvars$atmnet
rtnet <- mydata$depvars$rtnet
testfnet <- fnet[,,1]
testfnet[testfnet==10] <- NA
testrtnet <- rtnet[,,1]
testrtnet[testrtnet==10] <- NA
testatmnet <- atmnet[,,1]
testatmnet[testatmnet==10] <- NA

outdegreesf <- rowSums(testfnet, na.rm=TRUE)
indegreesf <- colSums(testfnet, na.rm=TRUE)

outdegreesrt <- rowSums(testrtnet, na.rm=TRUE)
indegreesrt <- colSums(testrtnet, na.rm=TRUE)

outdegreesatm <- rowSums(testatmnet, na.rm=TRUE)
indegreesatm <- colSums(testatmnet, na.rm=TRUE)

summary(lm(outdegreesf ~ as.factor(keyf$Partij)))
summary(lm(indegreesf ~ as.factor(keyf$Partij)))
#de enige grote partij die afwijkt is pvv.

summary(lm(outdegreesrt ~ as.factor(keyf$Partij)))
summary(lm(indegreesrt ~ as.factor(keyf$Partij)))
#de enige grote partij die afwijkt is d66.
#alter effect blijkt niet significant, dus weer geschrapt

summary(lm(outdegreesatm ~ as.factor(keyf$Partij)))
#de enige grote partij die afwijkt is d66 en GL.
summary(lm(indegreesatm ~ as.factor(keyf$Partij)))
# de enige grote partij die afwijkt is pvv

myeff <- getEffects( mydata )

#de enige grote partij die afwijkt is pvv.
myeff_m1 <- myeff
myeff_m1
myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "partij", name="fnet" )

# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "cda", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "cu", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "denk", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "d66", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "fvd", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "gl", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvda", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvdd", name="fnet" )
 myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvv", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "sgp", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "sp", name="fnet" )
# # myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "vvd", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "plus", name="fnet" )

# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "cda", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "cu", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "denk", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "d66", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "fvd", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "gl", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvda", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvdd", name="fnet" )
 myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvv", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "sgp", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "sp", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "vvd", name="fnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "plus", name="fnet" )

myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "partij", name="atmnet" )

# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "cda", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "cu", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "denk", name="atmnet" )
 myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "d66", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "fvd", name="atmnet" )
 myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "gl", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvda", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvdd", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvv", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "sgp", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "sp", name="atmnet" )
# # myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "vvd", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "plus", name="atmnet" )

# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "cda", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "cu", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "denk", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "d66", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "fvd", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "gl", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvda", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvdd", name="atmnet" )
 myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvv", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "sgp", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "sp", name="atmnet" )
# # myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "vvd", name="atmnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "plus", name="atmnet" )

myeff_m1 <- includeEffects(myeff_m1, sameX, interaction1 = "partij", name="rtnet" )

# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "cda", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "cu", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "denk", name="rtnet" )
 myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "d66", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "fvd", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "gl", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvda", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvdd", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "pvv", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "sgp", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "sp", name="rtnet" )
# # myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "vvd", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, egoX, interaction1 = "plus", name="rtnet" )

# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "cda", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "cu", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "denk", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "d66", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "fvd", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "gl", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvda", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvdd", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "pvv", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "sgp", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "sp", name="rtnet" )
# # myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "vvd", name="rtnet" )
# myeff_m1 <- includeEffects( myeff_m1, altX, interaction1 = "plus", name="rtnet" )

myeff_m1
save(myeff_m1, file="myeff_m1.Rdata")
}
#estimate model
{
# Estimate parameters
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff_m1.Rdata")
ansM1 <- siena07( myalgorithm, data = mydata, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1
ansM1b <- siena07( myalgorithm, data = mydata, prevAns=ansM1, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1b
ansM1c <- siena07( myalgorithm, data = mydata, prevAns=ansM1b, effects = myeff_m1, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM1c
save(ansM1c, file="ansM1c.Rdata")
}

###model 2: define myeff_m2 #structural effects
{
#effectsDocumentation(myeff)

myeff_m2 <- myeff_m1

#according to suggestion of rsiena manual
myeff_m2 <- includeEffects( myeff_m2, inPopSqrt, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, inPopSqrt, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, inPopSqrt, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, outActSqrt, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, outActSqrt, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, outActSqrt, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, outPopSqrt, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, outPopSqrt, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, outPopSqrt, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, transTrip, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, transTrip, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, transTrip, name="rtnet" )

#test for 3cycle if very significant, try transitive reciprocated triplets effects
myeff_m2 <- includeEffects( myeff_m2, cycle3, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, cycle3, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, cycle3, name="rtnet" )

#also for proximity
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, X, interaction1="afstand", name="rtnet" )

#we additionally for sharedPop
myeff_m2 <- includeEffects( myeff_m2, sharedPop, name="fnet" )
#myeff_m2 <- includeEffects( myeff_m2, sharedPop, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, sharedPop, name="rtnet" )

myeff_m2
save(myeff_m2, file="myeff_m2.Rdata")

}
#estimate model #note myeff_m2 is updated
{
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff_m2.Rdata")
load("ansM1c.Rdata")
ansM2 <- siena07( myalgorithm, data = mydata, prevAns=ansM1c, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM2
ansM2b <- siena07( myalgorithm, data = mydata, prevAns=ansM2, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM2b
ansM2c <- siena07( myalgorithm, data = mydata, prevAns=ansM2b, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM2c
save(ansM2c, file="ansM2c.Rdata")
#bij atm de ego/alter effecten er nog uit.

myeff_m2 <- includeEffects( myeff_m2, egoX, name="atmnet", interaction1='d66' ,include=FALSE)
myeff_m2 <- includeEffects( myeff_m2, egoX, name="atmnet", interaction1='gl' ,include=FALSE)
myeff_m2 <- includeEffects( myeff_m2, altX, name="atmnet", interaction1='pvv' ,include=FALSE)
myeff_m2
ansM2d <- siena07( myalgorithm, data = mydata, prevAns=ansM2c, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
myeff_m2 <- includeEffects( myeff_m2, altX, name="fnet", interaction1='pvv' ,include=FALSE)
ansM2e <- siena07( myalgorithm, data = mydata, prevAns=ansM2d, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM2e
ansM2f <- siena07( myalgorithm, data = mydata, prevAns=ansM2e, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM2f
ansM2g <- siena07( myalgorithm, data = mydata, prevAns=ansM2f, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM2g
save(ansM2g, file="ansM2g.Rdata")
save(myeff_m2, file="myeff_m2.Rdata")
}

###model 3: define myeff_m3 #byproduct hypo
{
myeff_m3 <- myeff_m2
#effectsDocumentation(myeff_m3)

#initial checks for ego/alt effects
summary(lm(outdegreesf ~ as.factor(keyf$Geslacht)))
summary(lm(indegreesf ~ as.factor(keyf$Geslacht)))
#geen geslacht effect

summary(lm(outdegreesrt ~ as.factor(keyf$Geslacht)))
summary(lm(indegreesrt ~ as.factor(keyf$Geslacht)))
#ego geslacht effect

summary(lm(outdegreesatm ~ as.factor(keyf$Geslacht)))
summary(lm(indegreesatm ~ as.factor(keyf$Geslacht)))
#geen geslacht effect

names(keyf)
summary(lm(outdegreesf ~ (keyf$GebJaar)))
summary(lm(indegreesf ~ (keyf$GebJaar)))
#ego lft effect

summary(lm(outdegreesrt ~ keyf$GebJaar))
summary(lm(indegreesrt ~ keyf$GebJaar))
#ego / alt lft effect

summary(lm(outdegreesatm ~ keyf$GebJaar))
summary(lm(indegreesatm ~ keyf$GebJaar))
#geen lft effect

summary(lm(outdegreesf ~ as.factor(keyf$EthMinZ)))
summary(lm(indegreesf ~ as.factor(keyf$EthMinZ)))
#geen minority effect

summary(lm(outdegreesrt ~ as.factor(keyf$EthMinZ)))
summary(lm(indegreesrt ~ as.factor(keyf$EthMinZ)))
#geen minority effect

summary(lm(outdegreesatm ~ as.factor(keyf$EthMinZ)))
summary(lm(indegreesatm ~ as.factor(keyf$EthMinZ)))
#geen minority effect

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="rtnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "vrouw", name="atmnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "vrouw", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "vrouw", name="atmnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="fnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="rtnet" )
myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, absDiffX , interaction1 = "lft", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "lft", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "lft", name="atmnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="fnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="fnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="rtnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="rtnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="rtnet" )

myeff_m3 <- includeEffects(myeff_m3, sameX, interaction1 = "ethminz", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, egoX, interaction1 = "ethminz", name="atmnet" )
#myeff_m3 <- includeEffects(myeff_m3, altX, interaction1 = "ethminz", name="atmnet" )

myeff_m3
save(myeff_m3, file="myeff_m3.Rdata")
}

#estimate parameters
{
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff_m3.Rdata")
load("ansM2g.Rdata")
ansM3 <- siena07( myalgorithm, data = mydata, prevAns=ansM2g, effects = myeff_m3, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM3
ansM3b <- siena07( myalgorithm, data = mydata, prevAns=ansM3, effects = myeff_m3, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM3b
ansM3c <- siena07( myalgorithm, data = mydata, prevAns=ansM3b, effects = myeff_m3, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM3c
ansM3d <- siena07( myalgorithm, data = mydata, prevAns=ansM3c, effects = myeff_m3, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM3d
save(ansM3c, file="ansM3c.Rdata")
}

###model 4: define myeff_m2 include additional controls
{
load("myeff_m3.Rdata")

myeff_m2 <- myeff_m3

#"kamerlid2016" "kabinet2016"  "pleklijst"    "pleklijst1"

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kabinet2016", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kabinet2016", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kabinet2016", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="kabinet2016", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kabinet2016", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kabinet2016", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", altX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst1", egoX, name="rtnet" )

myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, name="rtnet" )

myeff_m2
save(myeff_m2, file="myeff_m2.Rdata")
}

# estimate parameters
{

myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff_m2.Rdata")
load("ansM3c.Rdata")
ansM4 <- siena07( myalgorithm, data = mydata, prevAns=ansM3c, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4
ansM4b <- siena07( myalgorithm, data = mydata, prevAns=ansM4, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4b
ansM4c <- siena07( myalgorithm, data = mydata, prevAns=ansM4b, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4c
ansM4d <- siena07( myalgorithm, data = mydata, prevAns=ansM4c, effects = myeff_m2, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4d
save(ansM4d, file="ansM4d.Rdata")
}

#update myeff_m2 #remove covariate variables with t-value <1
{
myeff_m2 <- includeEffects( myeff_m2, interaction1="pvv", altX, include=FALSE, name="fnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pvv", egoX, include=FALSE, name="fnet" )
myeff_m2 <- includeEffects(myeff_m2, absDiffX , interaction1 = "lft" , include=FALSE, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="kamerlid2016", altX, include=FALSE, name="atmnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="pleklijst", diffX, include=FALSE, name="atmnet" )
myeff_m2 <- includeEffects(myeff_m2, sameX, interaction1 = "ethminz", include=FALSE, name="rtnet" )
myeff_m2 <- includeEffects( myeff_m2, interaction1="lft", egoX, include=FALSE, name="rtnet" )
myeff_m2 <- includeEffects(myeff_m2, absDiffX , interaction1 = "lft", include=FALSE, name="rtnet" )
myeff_m2
myeff_m2b <- myeff_m2
save(myeff_m2b, file="myeff_m2b.Rdata")
}

# estimate parameters
{
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff_m2b.Rdata")
load("ansM4d.Rdata")
ansM4e <- siena07( myalgorithm, data = mydata, prevAns=ansM4d, effects = myeff_m2b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4e
ansM4f <- siena07( myalgorithm, data = mydata, prevAns=ansM4e, effects = myeff_m2b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4f
ansM4g <- siena07( myalgorithm, data = mydata, prevAns=ansM4f, effects = myeff_m2b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4g
ansM4h <- siena07( myalgorithm, data = mydata, prevAns=ansM4g, effects = myeff_m2b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM4h
save(ansM4h, file="ansM4h.Rdata")
}
#ansm4e is best!
save(ansM4e, file="ansM4e.Rdata")
#maar f heeft een t voor otudegree atmnet
save(ansM4f, file="ansM4f.Rdata")
#iets fout gedaan maar wel beter model
save(ansM5, file="ansM4i.Rdata")
ansM4i <- ansM5
ansM4i
###model 5: crossnetwork effects
{
load("myeff_m2b.Rdata")
myeff5 <- myeff_m2b
#ik doe het een, ik doe het ander
myeff5 <- includeEffects( myeff5, crprod, interaction1="fnet", name="rtnet" )
myeff5 <- includeEffects( myeff5, crprod, interaction1="fnet", name="atmnet" )
myeff5 <- includeEffects( myeff5, crprod, interaction1="rtnet", name="fnet" )
myeff5 <- includeEffects( myeff5, crprod, interaction1="rtnet", name="atmnet" )
myeff5 <- includeEffects( myeff5, crprod, interaction1="atmnet", name="fnet" )
myeff5 <- includeEffects( myeff5, crprod, interaction1="atmnet", name="rtnet" )

#ik doe het een, jij doet het ander terug
myeff5 <- includeEffects( myeff5, crprodRecip, interaction1="fnet", name="rtnet" )
myeff5 <- includeEffects( myeff5, crprodRecip, interaction1="fnet", name="atmnet" )
myeff5 <- includeEffects( myeff5, crprodRecip, interaction1="rtnet", name="fnet" )
myeff5 <- includeEffects( myeff5, crprodRecip, interaction1="rtnet", name="atmnet" )
myeff5 <- includeEffects( myeff5, crprodRecip, interaction1="atmnet", name="fnet" )
myeff5 <- includeEffects( myeff5, crprodRecip, interaction1="atmnet", name="rtnet" )
myeff5

save(myeff5, file="myeff5.Rdata")
}

# model 5 estimate parameters
{
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff5.Rdata")
load("ansM4i.Rdata")
ansM5 <- siena07( myalgorithm, data = mydata, prevAns=ansM4f, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5
save(ansM5, file="ansM5.Rdata")
ansM5b <- siena07( myalgorithm, data = mydata, prevAns=ansM5, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5b
save(ansM5b, file="ansM5b.Rdata")
ansM5c <- siena07( myalgorithm, data = mydata, prevAns=ansM5b, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5c
save(ansM5c, file="ansM5c.Rdata")
ansM5d <- siena07( myalgorithm, data = mydata, prevAns=ansM5c, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5d
save(ansM5d, file="ansM5d.Rdata")

ansM5e <- siena07( myalgorithm, data = mydata, prevAns=ansM5d, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5e
save(ansM5e, file="ansM5e.Rdata")
ansM5f <- siena07( myalgorithm, data = mydata, prevAns=ansM5e, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5f
save(ansM5f, file="ansM5f.Rdata")
ansM5g <- siena07( myalgorithm, data = mydata, prevAns=ansM5f, effects = myeff5, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5g
save(ansM5g, file="ansM5g.Rdata")

}

#update parameters
{
load("myeff5.Rdata")
myeff5b <- myeff5
#ik doe het een, ik doe het ander
myeff5b <- includeEffects( myeff5b, crprod, interaction1="atmnet", name="fnet" , include=FALSE)

#ik doe het een, jij doet het ander terug
myeff5b <- includeEffects( myeff5b, crprodRecip, interaction1="atmnet", name="fnet" , include=FALSE)

myeff5b

save(myeff5b, file="myeff5b.Rdata")
}


# reestimate model 5 estimate parameters
{
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff5b.Rdata")
load("ansM5e.Rdata")
ansM5h <- siena07( myalgorithm, data = mydata, prevAns=ansM5e, effects = myeff5b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5h
save(ansM5h, file="ansM5h.Rdata")
ansM5i <- siena07( myalgorithm, data = mydata, prevAns=ansM5h, effects = myeff5b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5i
save(ansM5i, file="ansM5i.Rdata")
ansM5j <- siena07( myalgorithm, data = mydata, prevAns=ansM5i, effects = myeff5b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5j
save(ansM5j, file="ansM5j.Rdata")
ansM5k <- siena07( myalgorithm, data = mydata, prevAns=ansM5j, effects = myeff5b, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM5k
save(ansM5k, file="ansM5k.Rdata")


}


###model 6 : time heterogeneity

{
tt <- sienaTimeTest(ansM5i)
#plot(tt, effects=1:70)
tt$EffectTest
load("myeff5b.Rdata")
myeff6 <- myeff5b
myeff6 <- includeTimeDummy(myeff6, sameX, interaction1 = "partij", name="atmnet", timeDummy="2")
myeff6 <- includeTimeDummy(myeff6, sameX, interaction1 = "partij", name="rtnet", timeDummy="2")
myeff6
save(myeff6, file="myeff6.Rdata")
}

# estimate parameters Model 6
{
#ansM5i best
myalgorithm <- sienaAlgorithmCreate( projname = 'test')
load("myeff6.Rdata")
load("ansM5i.Rdata")
ansM6 <- siena07( myalgorithm, data = mydata, prevAns=ansM5i, effects = myeff6, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM6
save(ansM6, file="ansM6.Rdata")
ansM6b <- siena07( myalgorithm, data = mydata, prevAns=ansM6, effects = myeff6, useCluster=TRUE, nbrNodes=4, initC=TRUE, batch=TRUE)
ansM6b
save(ansM6b, file="ansM6.Rdata")

}

#prepare output table
load("ansM1c.Rdata")
load("ansM2g.Rdata")
load("ansM3c.Rdata")
load("ansM4i.Rdata")
ansM4i <- ansM5
load("ansM5i.Rdata")
load("ansM6.Rdata")
ansM6

fanscsv <- function(ans=ans, filename="ans.csv") {
	ans1_mat <- matrix(NA, nrow=length(ans$effects[,2]),ncol=3)
	row.names(ans1_mat) <- ans$effects[,2]
	ans1_mat[,1] <- (ans$theta)
	ans1_mat[,2] <- (ans$se)
	ans1_mat[,3] <- (ans$tconv)
	ans1_mat <- rbind(ans1_mat, c(ans$tconv.max))
	row.names(ans1_mat)[length(row.names(ans1_mat))] <- "Overall maximum convergence ratio:"
	colnames(ans1_mat) <- c("Estimate", "Standard Error", "Convergence t-ratio")
	print(ans1_mat)
	write.csv(ans1_mat, filename)
}

fanscsv(ansM2g, "ansM2.csv")

ans1_mat
?write.csv

ans1_mat[length(ansM1c$effects[,2])+1,1] <- ansM1c$tconv.max

ans1_mat

colnames(ans1_mat) <- c("effect name", "Estimate", "Standard Error", "Convergence t-ratio")
ans1_mat
ansM1c

colnames(ans1_mat) <- c("effect name", "Estimate", "Standard Error", "Convergence t-ratio")

ansM1c$theta
ansM1c$effects[,2]
ansM1c$se

---> 


