---
title: "Replication package-Descriptives"
author: '[Jochem Tolsma](https://www.jochemtolsma.nl) - Radboud University / University of Groningen, the Netherlands'
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    toc:  true
    toc_float: true
    number_sections: false
    code_folding: hide
    code_download: yes
---

```{r globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, echo=FALSE, class.source=c("test"), results = "hold", class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r colorize, echo=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
            x)
  } else x
}

```

```{r klippy, echo=FALSE, include=TRUE, eval=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{css, echo=FALSE}
pre.test {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
}

pre.test2 {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
  background-color: white;
  color: rgb(201, 76, 76);
}


h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
}


```



------------------------------------------------------------------------


# Intro  


This [website](https://jochemtolsma.github.io/Twitter/) is a replication package for the paper "**How Twitter divides the Dutch parliament: Segregation along party lines and social dimensions in the following, @-mentions and retweets Twitter Networks of Dutch MPs**" by @Tolsma2021.  

It contains R code to replicate all Tables/Figures/Appendix in the manuscript.

To copy the code click the button in the upper right corner of the code-chunks.

Use the top menu to navigate to the section of interest. 

The source code of this website can be found on [Github](https://github.com/JochemTolsma/Twitter)

Questions can be addressed to [Jochem Tolsma](mailto:jochem.tolsma@ru.nl).

---  


```{r}
      
print(Sys.setenv(BEARER_TOKEN = "AAAAAAAAAAAAAAAAAAAAALmelAEAAAAApWIeFQimixSSF4o2CQcaPqV4KCM%3DhSSOM4sNuNcD03hHzs5tpwm68vsJqIfycrOEBzbwtnUnzgfNG7"))

print(Sys.setenv(R_TEST = "testit", "A+C" = 123))  # `A+C` could also be used
Sys.unsetenv("R_TEST")
Sys.getenv("BEARER_TOKEN")


```

```{r}
      
install.packages("httr")
install.packages("jsonlite")
install.packages("dplyr")
library("jsonlite")
    
```

```{r}
      
bearer_token <- Sys.getenv("BEARER_TOKEN")
headers <- c(`Authorization` = sprintf('Bearer %s', bearer_token))

    
```

```{r}
      
handle <- "TomWGvdMeer,TolsmaJochem"

url_handle <- sprintf('https://api.twitter.com/2/users/by?usernames=%s', handle)

    
```

```{r}
      
params <- list(`user.fields` = 'description,created_at',
               `expansions` = 'pinned_tweet_id',
               `tweet.fields` = 'created_at')

    
```

```{r}
      
response <-
  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
print(obj)

    
```

Finding tweets
```{r}
url_handle <- sprintf('https://api.twitter.com/2/tweets/search/recent')


# params <- list(`query`='from:TomWGvdMeer',
#                `user.fields` = 'description,created_at',
#                `expansions` = 'author_id',
#                `tweet.fields` = 'created_at')

params <- list(`query`='from:NielsSpierings')


response <-
  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
#print(obj)


json_data1 <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
View(json_data1)

```

finding retweets of Tom

```{r}
url_handle <- sprintf('https://api.twitter.com/2/tweets/search/recent')


# params <- list(`query`='from:TomWGvdMeer',
#                `user.fields` = 'description,created_at',
#                `expansions` = 'author_id',
#                `tweet.fields` = 'created_at')

params <- list(`query`='from:NielsSpierings is:retweet')


response <-
  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
#print(obj)


json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
View(json_data)

```


```{r}
url_handle <- sprintf('https://api.twitter.com/2/tweets/search/recent')
params <- list(`query`= '@TomWGvdMeer')  
response <-
  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
#print(obj)

json_data3 <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
View(json_data3)

```

